SMT-Based Context-Bounded Model Checking for Embedded Systems: State of the Art and Future Trends

### 2016-03-21 paper.tex
add figure 2

Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health with serious consequences.

@@

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation~\cite{Behrend15,Lettnin09}. In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system's functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness; additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions; and
	\item legacy designs.%, which are usually developed with low-level languages.
\end{enumerate}

>>>>

Figure~\ref{intelligent-product} shows examples of embedded systems, which consist of a human-machine interface ({\it e.g.}, keyboard and LCD) and an instrumentation interface ({\it e.g.}, sensor, network, and actuator). Indeed, many current embedded systems, such as unmanned aerial vehicles (UAVs)~\cite{groza2015formal} and medical monitoring systems~\cite{Cordeiro09}, become interesting solutions only if they can reliably perform their target tasks. For instance, UAVs are a trend on military missions, due to the absence of pilots; however, an incorrect plan execution may also cost human-lives, which is unacceptable. In addition, wrong disease diagnosis or condition-evaluation reports have the potential to compromise patients' health with serious consequences.
%
\begin{figure}[!t]
	\centering
	\includegraphics[scale=0.35]{figure1.eps}
	\caption{Embedded system is part of a well-specified larger system (intelligent product).}
	\label{intelligent-product}
\end{figure}

@@

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation~\cite{Behrend15,Lettnin09} as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure2.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system's functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness; additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions; and
	\item legacy designs.%, which are usually developed with low-level languages.
\end{enumerate}
